---
title: "Homework 2"
author: "Brent Rappaport"
date: "September 12, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(rmarkdown)
library(kableExtra)
library(tidyr)
library(ggplot2)
library(psych)
library(lme4)
library(broom)
library(merTools)
library(foreach)
library(sjPlot)

data_wide <- read.csv("/Users/BrentRappaport/Box Sync/WashU/Classes/Longtudinal Methods/1-descriptives-and-graphs-brappaport/Rappaport_data.csv")

data_long <- data_wide %>% 
  gather(c(-ID,-sex,-T1_ACES_sum,-ethin,-T1Income_to_Need,-IQ), 
         key = "time", value = "value") %>% 
  separate(time, into = c("variable", "wave")) %>%
  spread(variable,value)

data_long$wave <- as.integer(data_long$wave)
```


# Question 1
```{r Question 1}
model1 <- lm(PPeerScale ~ age, data=data_long)
summary(model1)
```
Average intercept is 61.02 and average slope is 0.11.

# Question 2
```{r Question 2}
model2 <- lmer(PPeerScale ~ 1 + (1 | ID), data=data_long)
summary(model2)

# Calculate ICC
42.93/(42.93+38.33)

model2.aug <- augment(model2, data_long)

ggplot(model2.aug,aes(.resid,.fitted,group=ID)) +
  geom_point(alpha=1) +
  theme(text=element_text(lineheight=1, face="bold", size=15), 
        legend.position="none")
```

# Question 3
```{r Question 3}
model3 <- lmer(PPeerScale ~ age + (1 | ID), data=data_long)
summary(model3)
```
The esimates of the fixed effect for the Intercept doesn't change much, however now that age is being included as a fixed effect, we can get a sense of the average change over time in parent reported Peer scores. That is, for ever 1 year, participants increase an average of 0.15 in their score.

```{r Question 3 cont1}
print(c(sigma(model2),sigma(model3)))
```
The residual standard error (sigma here), doesn't change much between the two models, but does decrease when age is introduced as a fixed effect.

```{r Question 3 cont2}
plot3_table <- FEsim(model2)
plot3_table[2:3,] <- FEsim(model3)
plot3_table[1] <- c("Model2 Intercept","Model3 Intercept","Model3 Age")

plot3_table$ci <- 1.96*plot3_table$sd

ggplot(plot3_table,aes(x=term,y=mean)) +
  geom_point() +
  geom_errorbar(aes(ymin=mean-ci,ymax=mean+ci),width=0.2)
```

# Question 4
```{r Question 4}
model4 <- lmer(PPeerScale ~ age + (age | ID), data=data_long)
print(c(sigma(model3),sigma(model4)))
anova(model3,model4)
```
Adding the random slope improves fit, according to the AIC, BIC, and likelihood ratio test, while also considerably lowering the residual standard error (from `r sigma(model3)` to `r sigma(model4)`).

# Question 5
```{r Question 5}
summary(model4)
```
The correlation means that there is a negative correlation between the intercept and the slope, such that the lower the intercept, the higher the slope will be.

# Question 6
```{r Question 6}
model4_re.sim <- REsim(model4)
p1.gg <- model4_re.sim %>% 
  filter(term == c("(Intercept)","age")) 

# Intercept
ggplot(p1.gg[p1.gg$term %in% "(Intercept)",], aes(mean)) +
  geom_density()

# Age
ggplot(p1.gg[p1.gg$term %in% "age",], aes(mean)) +
  geom_density()
```

# Question 7
```{r Question 7}
plotREsim(model4_re.sim)
```
No, there are no obvious outliers in terms of unusually large standard errors around the intercept or slopes.

# Question 8
```{r Question 8}
PT <- predictInterval(merMod=model4, newdata=data_long, level=0.9, n.sims=100, stat="mean", 
                      include.resid.var=TRUE)
PT_plot <- data_long; PT_plot[,15:17] <- PT

#example graph using ONLY FIRST 10 participants and fitted scores with confidence bands
ggplot(PT_plot[1:80,],aes(age,fit,group=ID)) +
  geom_line(alpha=0.6) +
  stat_smooth(aes(group=1),method="lm", color="sky blue") +
  geom_ribbon(aes(ymin=lwr,ymax=upr),linetype=2,alpha=0.1) +
  labs(x="Age",y="fitted Parent-report Peer Scale Score")

#graphed using ALL participants and fitted scores with confidence bands
ggplot(PT_plot,aes(age,fit,group=ID)) +
  geom_line(alpha=0.6) +
  stat_smooth(aes(group=1),method="lm", color="sky blue") +
  geom_ribbon(aes(ymin=lwr,ymax=upr),linetype=2,alpha=0.1) +
  labs(x="Age",y="fitted Parent-report Peer Scale Score")
```