---
title: "Homework 3"
author: "Brent Rappaport"
date: "September 26, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#clear workspace
#removes variables from memory (upper right pane)
rm(list=ls(all=TRUE)) 

library(knitr)
library(rmarkdown)
library(kableExtra)
library(tidyr)
library(ggplot2)
library(psych)
library(lme4)
library(broom)
library(merTools)
library(foreach)
library(sjPlot)
library(mltools)

data_wide <- read.csv("/Users/BrentRappaport/Box Sync/WashU/Classes/Longtudinal Methods/1-descriptives-and-graphs-brappaport/Rappaport_data.csv")

data_wide$sex_01 <- data_wide$sex-1

data_wide$sex_c <- scale(data_wide$sex_01, center=T, scale=F)
data_wide$T1Income_to_Need_c <- scale(data_wide$T1Income_to_Need, center=T, scale=F)

data_long <- data_wide %>% 
  gather(c(-ID,-sex,-sex_01,-sex_c,-T1_ACES_sum,-ethin,-T1Income_to_Need,-T1Income_to_Need_c,-IQ), 
         key = "time", value = "value") %>% 
  separate(time, into = c("variable", "wave")) %>%
  spread(variable,value)

data_long$wave <- as.integer(data_long$wave)
```


# Question 1
```{r Question 1}
## Add a nominal covariate into the model (sex)

#Predicting intercept
model1a <- lmer(PPeerScale ~ age + sex_01 + (age | ID), data=data_long)
tidy(model1a)

#Predicting intercept and slope
model1b <- lmer(PPeerScale ~ age + sex_01 + age:sex_01 + (age | ID), data=data_long)
tidy(model1b)

#Predicting intercept and slope, with sex centerd
model1c <- lmer(PPeerScale ~ age + sex_c + age:sex_c + (age | ID), data=data_long)
tidy(model1c)

model1c_t <- lmer(TPeerScale ~ age + sex_c + age:sex_c + (age | ID), data=data_long)
```
Centering the nominal covariate (sex) did not affect the model, except for the fixed effect estimate of age. This makes sense, since, with the introduction of the interaction term introduced in model b now means that the fixed effect of age is representative of the predicted change in PPeer (x) for every unit change in age (y), when sex =0. Prior to centering, this then represented the mean change for males (dummy coded as 0), but after centering indicates the average mean change across both genders.


# Question 2
```{r Question 2}
## Add a continuous time-invariant covariate into the model (SES=T1Income_to_Need)

#Predicting intercept
model2a <- lmer(PPeerScale ~ age + T1Income_to_Need + (age | ID), data=data_long)
tidy(model2a)

#Predicting intercept and slope
model2b <- lmer(PPeerScale ~ age + T1Income_to_Need + age:T1Income_to_Need + (age | ID), data=data_long)
tidy(model2b)

#Predicting intercept and slope, with SES centerd
model2c <- lmer(PPeerScale ~ age + T1Income_to_Need_c + age:T1Income_to_Need_c + (age | ID), data=data_long)
tidy(model2c)

model2c_t <- lmer(TPeerScale ~ age + T1Income_to_Need_c + age:T1Income_to_Need_c + (age | ID),
                  data=data_long)
```
Centering the covariate affected the Intercept and age fixed effects estimates, since (similar to above), they go from being interpreted as the average intercept and average change in PPeer with age of the male group to the average intercept and change in PPeer with age of all subjects.


# Question 3
```{r Question 3}
sjp.lmer(model1c, type="pred", facet.grid=F,
         vars = c("age", "sex_c"))

sjp.lmer(model1c_t, type="pred", facet.grid=F,
         vars = c("age", "sex_c"))

sjp.int(model2c, 
        type = "eff",
        mdrt.values = "quart",
        swap.pred=T,
        p.value=.05)

sjp.int(model2c_t, 
        type = "eff",
        mdrt.values = "quart",
        swap.pred=T,
        p.value=.05)
```


# Question 4
```{r Question 4}
model1c_ci <- confint(model1c, level=.95, oldNames=F, method="boot", nsim=100)
model1c_ci[c(1,3,5:8),]

model2c_ci <- confint(model2c, level=.95, oldNames=F, method="boot", nsim=100)
model2c_ci[c(1,3,5:8),]
```


# Question 5
```{r Question 5}
model5 <- lmer(PPeerScale ~ age*T1Income_to_Need_c + age*sex_01 + (age | ID), data=data_long)
model5_t <- lmer(TPeerScale ~ age*T1Income_to_Need_c + age*sex_01 + (age | ID), data=data_long)

tidy(model5)
tidy(model2c)

sjp.int(model5, 
        type = "eff",
        mdrt.values = "quart",
        swap.pred=T,
        p.value=.05)

sjp.int(model5_t, 
        type = "eff",
        mdrt.values = "quart",
        swap.pred=T,
        p.value=.05)
```
