---
title: "SEM"
author: "Brent Rappaport"
date: "October 30, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval = T, cache = T, warning = F, message = T)
rm(list=ls())
library(psych)
library(tidyverse)
library(sjPlot)
library(broom)
library(lme4)
library(lavaan)
library(lattice)
library(semPlot)
```

##Load in data
```{r load data}
data_wide <- read.csv("/Users/BrentRappaport/Box Sync/WashU/Classes/Longtudinal Methods/1-descriptives-and-graphs-brappaport/Rappaport_data.csv")
data_wide <- data_wide[,-1]

#Make sex_01 a binary variable where 0=Male and 1=Female
data_wide$sex_01 <- data_wide$sex-1

#Make sex_c a factor variable
data_wide$sex_c <- ifelse(data_wide$sex_01==0,"Male","Female")
data_wide$sex_c <- as.factor(data_wide$sex_c)

#Center SES
data_wide$T1Income_to_Need_c <- as.numeric(scale(data_wide$T1Income_to_Need, center=T, scale=F))

#Make age0_ a variable of age from beginning of study (relative age to beginning), rather than aboslute age
data_wide <- data_wide %>%
  mutate(age0_1 = age_1 - age_1,
         age0_3 = age_3 - age_1,
         age0_5 = age_5 - age_1,
         age0_10 = age_10 - age_1,
         age0_12 = age_12 - age_1,
         age0_14 = age_14 - age_1,
         age0_16 = age_16 - age_1,
         age0_18 = age_18 - age_1)

#Convert data to long form
data_long <- data_wide %>% 
  gather(c(-ID,-sex,-sex_01,-sex_c,-T1_ACES_sum,-ethin,-T1Income_to_Need,-T1Income_to_Need_c,-IQ), 
         key = "time", value = "value") %>% 
  separate(time, into = c("variable", "wave")) %>%
  spread(variable,value)

data_long$wave <- as.integer(data_long$wave)

#sort by id
data_long <- data_long[order(data_long$ID),] 
```

## Question 1
```{r Question 1 Marker Variable}
#1. Specify your model: Marker variable approach
mod.1 <- 'peer =~ PPeerScale_1 + TPeerScale_1
          aggression =~ PAggScale_1 + TAggScale_1
          prosocial =~ PProScale_1 + TProScale_1'

#2. Fit the model
fit.1 <- cfa(mod.1, data=data_wide)
# other functions include sem, growth, and lavaan. All have different defaults (See below). we will use growth a lot. 

#3. Display the summary output
summary(fit.1, fit.measures=TRUE)
```

```{r Question 1 Fixed Factor}
#Fixed factor approach
fit.2 <- cfa(mod.1, std.lv=TRUE, data=data_wide)

summary(fit.2, fit.measures=TRUE, standardized=TRUE)
```

```{r Question 1 Effects Coding}
#Effects coding approach
mod.3 <- 'peer =~ NA*PPeerScale_1 + pe1*PPeerScale_1 + pe2*TPeerScale_1
          aggression =~ NA*PAggScale_1 +a1*PAggScale_1 + a2*TAggScale_1
          prosocial =~ NA*PProScale_1 + pr1*PProScale_1 + pr2*TProScale_1

     pe1 == 2 - pe2
     a1 == 2 - a2
     pr1 == 2 - pr2
' 

fit.3 <- cfa(mod.3, data=data_wide) 
summary(fit.3, fit.measures=TRUE, standardized=TRUE) 

anova(fit.1,fit.3)
```
Across the three models, the estimates of the latent variables (or the factor loadings) obviously change, but consistently indicate a larger factor loading teacher report onto the latent variable than parent report. The std.all does not change across models, since it is the standardized indicator of how much variance is being accounted for by the latent variable.

In the fixed factor model, the covariance estimates indicate the correlation between the latent variables, here indicating that the Peer and Prosocial variables are highly correlated (0.884), while Peer and Aggression and Aggression and Prosocial are moderately related (0.633 and 0.546, repectively).

The variance estimates for the latent variables also change. In the first model (marker variable approach), the estimates for the latent variables indicate that they are accounting for substantial variance in the scores. In the second model (fixed factor), the variance estimates are fixed to 1, and the variances of the residuals remains unchanged. In the third model (effects coding), the standarized estimates (std.all) are fixed to 1.


## Question 2
The RMSEA is above 0.1 (0.133), indicating a poor fit, however the SRMR is 0.056 indicating an acceptable fit. The CFI and TFI additionally fall below 0.90 at 0.879 and 0.698, respectively, suggesting a less than optimal fit. The model indicates 15 degrees of freedom indicating that is it overidentified (good).


## Question 3
```{r Question 3a}
#Longitudinal CFA
mod.4.full <- '
peer1 =~ PPeerScale_1 + TPeerScale_1
peer2 =~ PPeerScale_3 + TPeerScale_3
peer3 =~ PPeerScale_5 + TPeerScale_5
peer4 =~ PPeerScale_10 + TPeerScale_10
peer5 =~ PPeerScale_12 + TPeerScale_12
peer6 =~ PPeerScale_14 + TPeerScale_14
peer7 =~ PPeerScale_16 + TPeerScale_16
peer8 =~ PPeerScale_18 + TPeerScale_18

agg1 =~ PAggScale_1 + TAggScale_1
agg2 =~ PAggScale_3 + TAggScale_3
agg3 =~ PAggScale_5 + TAggScale_5
agg4 =~ PAggScale_10 + TAggScale_10
agg5 =~ PAggScale_12 + TAggScale_12
agg6 =~ PAggScale_14 + TAggScale_14
agg7 =~ PAggScale_16 + TAggScale_16
agg8 =~ PAggScale_18 + TAggScale_18

pro1 =~ PProScale_1 + TProScale_1
pro2 =~ PProScale_3 + TProScale_3
pro3 =~ PProScale_5 + TProScale_5
pro4 =~ PProScale_10 + TProScale_10
pro5 =~ PProScale_12 + TProScale_12
pro6 =~ PProScale_14 + TProScale_14
pro7 =~ PProScale_16 + TProScale_16
pro8 =~ PProScale_18 + TProScale_18

## correlated residuals across time
PPeerScale_1 ~~ PPeerScale_3 + PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14 +
PPeerScale_16 + PPeerScale_18
PPeerScale_3 ~~ PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14 +
PPeerScale_16 + PPeerScale_18
PPeerScale_5 ~~ PPeerScale_10 + PPeerScale_12 + PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_10 ~~ PPeerScale_12 + PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_12 ~~ PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_14 ~~ PPeerScale_16 + PPeerScale_18
PPeerScale_16 ~~ PPeerScale_18

TPeerScale_1 ~~ TPeerScale_3 + TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14 +
TPeerScale_16 + TPeerScale_18
TPeerScale_3 ~~ TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14 +
TPeerScale_16 + TPeerScale_18
TPeerScale_5 ~~ TPeerScale_10 + TPeerScale_12 + TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_10 ~~ TPeerScale_12 + TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_12 ~~ TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_14 ~~ TPeerScale_16 + TPeerScale_18
TPeerScale_16 ~~ TPeerScale_18

PAggScale_1 ~~ PAggScale_3 + PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14 +
PAggScale_16 + PAggScale_18
PAggScale_3 ~~ PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14 +
PAggScale_16 + PAggScale_18
PAggScale_5 ~~ PAggScale_10 + PAggScale_12 + PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_10 ~~ PAggScale_12 + PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_12 ~~ PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_14 ~~ PAggScale_16 + PAggScale_18
PAggScale_16 ~~ PAggScale_18

TAggScale_1 ~~ TAggScale_3 + TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14 +
TAggScale_16 + TAggScale_18
TAggScale_3 ~~ TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14 +
TAggScale_16 + TAggScale_18
TAggScale_5 ~~ TAggScale_10 + TAggScale_12 + TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_10 ~~ TAggScale_12 + TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_12 ~~ TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_14 ~~ TAggScale_16 + TAggScale_18
TAggScale_16 ~~ TAggScale_18

PProScale_1 ~~ PProScale_3 + PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14 +
PProScale_16 + PProScale_18
PProScale_3 ~~ PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14 +
PProScale_16 + PProScale_18
PProScale_5 ~~ PProScale_10 + PProScale_12 + PProScale_14 + PProScale_16 + PProScale_18
PProScale_10 ~~ PProScale_12 + PProScale_14 + PProScale_16 + PProScale_18
PProScale_12 ~~ PProScale_14 + PProScale_16 + PProScale_18
PProScale_14 ~~ PProScale_16 + PProScale_18
PProScale_16 ~~ PProScale_18

TProScale_1 ~~ TProScale_3 + TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14 +
TProScale_16 + TProScale_18
TProScale_3 ~~ TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14 +
TProScale_16 + TProScale_18
TProScale_5 ~~ TProScale_10 + TProScale_12 + TProScale_14 + TProScale_16 + TProScale_18
TProScale_10 ~~ TProScale_12 + TProScale_14 + TProScale_16 + TProScale_18
TProScale_12 ~~ TProScale_14 + TProScale_16 + TProScale_18
TProScale_14 ~~ TProScale_16 + TProScale_18
TProScale_16 ~~ TProScale_18
'

mod.4 <- '
peer1 =~ PPeerScale_1 + TPeerScale_1
peer2 =~ PPeerScale_3 + TPeerScale_3
peer3 =~ PPeerScale_5 + TPeerScale_5
peer4 =~ PPeerScale_10 + TPeerScale_10
peer5 =~ PPeerScale_12 + TPeerScale_12
peer6 =~ PPeerScale_14 + TPeerScale_14

agg1 =~ PAggScale_1 + TAggScale_1
agg2 =~ PAggScale_3 + TAggScale_3
agg3 =~ PAggScale_5 + TAggScale_5
agg4 =~ PAggScale_10 + TAggScale_10
agg5 =~ PAggScale_12 + TAggScale_12
agg6 =~ PAggScale_14 + TAggScale_14

pro1 =~ PProScale_1 + TProScale_1
pro2 =~ PProScale_3 + TProScale_3
pro3 =~ PProScale_5 + TProScale_5
pro4 =~ PProScale_10 + TProScale_10
pro5 =~ PProScale_12 + TProScale_12
pro6 =~ PProScale_14 + TProScale_14

## correlated residuals across time
PPeerScale_1 ~~ PPeerScale_3 + PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_3 ~~ PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_5 ~~ PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_10 ~~ PPeerScale_12 + PPeerScale_14
PPeerScale_12 ~~ PPeerScale_14

TPeerScale_1 ~~ TPeerScale_3 + TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_3 ~~ TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_5 ~~ TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_10 ~~ TPeerScale_12 + TPeerScale_14
TPeerScale_12 ~~ TPeerScale_14

PAggScale_1 ~~ PAggScale_3 + PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_3 ~~ PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_5 ~~ PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_10 ~~ PAggScale_12 + PAggScale_14
PAggScale_12 ~~ PAggScale_14

TAggScale_1 ~~ TAggScale_3 + TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_3 ~~ TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_5 ~~ TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_10 ~~ TAggScale_12 + TAggScale_14
TAggScale_12 ~~ TAggScale_14

PProScale_1 ~~ PProScale_3 + PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14
PProScale_3 ~~ PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14
PProScale_5 ~~ PProScale_10 + PProScale_12 + PProScale_14
PProScale_10 ~~ PProScale_12 + PProScale_14
PProScale_12 ~~ PProScale_14

TProScale_1 ~~ TProScale_3 + TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14
TProScale_3 ~~ TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14
TProScale_5 ~~ TProScale_10 + TProScale_12 + TProScale_14
TProScale_10 ~~ TProScale_12 + TProScale_14
TProScale_12 ~~ TProScale_14
'

#fit.4 <- cfa(mod.4, data=data_wide, missing="ML", std.lv=TRUE)
#inspect(fit.4,"cov.lv")

#summary(fit.4, standardized=TRUE, fit.measures=TRUE)
```
Received warning that covariance matrix was not positive definite.

```{r Question 3b}
#Longitudinal cross-lagged model predicting later times by previous times (autoregressive)
mod.5.full <- '
##define latent variables
peer1 =~ L1*PPeerScale_1 + L2*TPeerScale_1
peer2 =~ L1*PPeerScale_3 + L2*TPeerScale_3
peer3 =~ L1*PPeerScale_5 + L2*TPeerScale_5
peer4 =~ L1*PPeerScale_10 + L2*TPeerScale_10
peer5 =~ L1*PPeerScale_12 + L2*TPeerScale_12
peer6 =~ L1*PPeerScale_14 + L2*TPeerScale_14
peer7 =~ L1*PPeerScale_16 + L2*TPeerScale_16
peer8 =~ L1*PPeerScale_18 + L2*TPeerScale_18

agg1 =~ L1*PAggScale_1 + L2*TAggScale_1
agg2 =~ L1*PAggScale_3 + L2*TAggScale_3
agg3 =~ L1*PAggScale_5 + L2*TAggScale_5
agg4 =~ L1*PAggScale_10 + L2*TAggScale_10
agg5 =~ L1*PAggScale_12 + L2*TAggScale_12
agg6 =~ L1*PAggScale_14 + L2*TAggScale_14
agg7 =~ L1*PAggScale_16 + L2*TAggScale_16
agg8 =~ L1*PAggScale_18 + L2*TAggScale_18

pro1 =~ L1*PProScale_1 + L2*TProScale_1
pro2 =~ L1*PProScale_3 + L2*TProScale_3
pro3 =~ L1*PProScale_5 + L2*TProScale_5
pro4 =~ L1*PProScale_10 + L2*TProScale_10
pro5 =~ L1*PProScale_12 + L2*TProScale_12
pro6 =~ L1*PProScale_14 + L2*TProScale_14
pro7 =~ L1*PProScale_16 + L2*TProScale_16
pro8 =~ L1*PProScale_18 + L2*TProScale_18

## free latent variances at later times (only set the scale once)
peer2 ~~ NA*peer2
peer3 ~~ NA*peer3
peer4 ~~ NA*peer4
peer5 ~~ NA*peer5
peer6 ~~ NA*peer6
peer7 ~~ NA*peer7
peer8 ~~ NA*peer8

agg2 ~~ NA*agg2
agg3 ~~ NA*agg3
agg4 ~~ NA*agg4
agg5 ~~ NA*agg5
agg6 ~~ NA*agg6
agg7 ~~ NA*agg7
agg8 ~~ NA*agg8

pro2 ~~ NA*pro2
pro3 ~~ NA*pro3
pro4 ~~ NA*pro4
pro5 ~~ NA*pro5
pro6 ~~ NA*pro6
pro7 ~~ NA*pro7
pro8 ~~ NA*pro8

peer1 ~~ agg1 + pro1
agg1 ~~ pro1
peer2 ~~ agg2 + pro2
agg2 ~~ pro2
peer3 ~~ agg3 + pro3
agg3 ~~ pro3
peer4 ~~ agg4 + pro4
agg4 ~~ pro4
peer5 ~~ agg5 + pro5
agg5 ~~ pro5
peer6 ~~ agg6 + pro6
agg6 ~~ pro6
peer7 ~~ agg7 + pro7
agg7 ~~ pro7
peer8 ~~ agg8 + pro8
agg8 ~~ pro8

## directional regression paths
peer2 ~ peer1 + agg1 + pro1
agg2 ~ peer1 + agg1 + pro1
pro2 ~ peer1 + agg1 + pro1

peer3 ~ peer2 + agg2 + pro2
agg3 ~ peer2 + agg2 + pro2
pro3 ~ peer2 + agg2 + pro2

peer4 ~ peer3 + agg3 + pro3
agg4 ~ peer3 + agg3 + pro3
pro4 ~ peer3 + agg3 + pro3

peer5 ~ peer4 + agg4 + pro4
agg5 ~ peer4 + agg4 + pro4
pro5 ~ peer4 + agg4 + pro4

peer6 ~ peer5 + agg5 + pro5
agg6 ~ peer5 + agg5 + pro5
pro6 ~ peer5 + agg5 + pro5

peer7 ~ peer6 + agg6 + pro6
agg7 ~ peer6 + agg6 + pro6
pro7 ~ peer6 + agg6 + pro6

peer8 ~ peer7 + agg7 + pro7
agg8 ~ peer7 + agg7 + pro7
pro8 ~ peer7 + agg7 + pro7

## correlated residuals across time
PPeerScale_1 ~~ PPeerScale_3 + PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14 +
PPeerScale_16 + PPeerScale_18
PPeerScale_3 ~~ PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14 +
PPeerScale_16 + PPeerScale_18
PPeerScale_5 ~~ PPeerScale_10 + PPeerScale_12 + PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_10 ~~ PPeerScale_12 + PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_12 ~~ PPeerScale_14 + PPeerScale_16 + PPeerScale_18
PPeerScale_14 ~~ PPeerScale_16 + PPeerScale_18
PPeerScale_16 ~~ PPeerScale_18

TPeerScale_1 ~~ TPeerScale_3 + TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14 +
TPeerScale_16 + TPeerScale_18
TPeerScale_3 ~~ TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14 +
TPeerScale_16 + TPeerScale_18
TPeerScale_5 ~~ TPeerScale_10 + TPeerScale_12 + TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_10 ~~ TPeerScale_12 + TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_12 ~~ TPeerScale_14 + TPeerScale_16 + TPeerScale_18
TPeerScale_14 ~~ TPeerScale_16 + TPeerScale_18
TPeerScale_16 ~~ TPeerScale_18

PAggScale_1 ~~ PAggScale_3 + PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14 +
PAggScale_16 + PAggScale_18
PAggScale_3 ~~ PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14 +
PAggScale_16 + PAggScale_18
PAggScale_5 ~~ PAggScale_10 + PAggScale_12 + PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_10 ~~ PAggScale_12 + PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_12 ~~ PAggScale_14 + PAggScale_16 + PAggScale_18
PAggScale_14 ~~ PAggScale_16 + PAggScale_18
PAggScale_16 ~~ PAggScale_18

TAggScale_1 ~~ TAggScale_3 + TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14 +
TAggScale_16 + TAggScale_18
TAggScale_3 ~~ TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14 +
TAggScale_16 + TAggScale_18
TAggScale_5 ~~ TAggScale_10 + TAggScale_12 + TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_10 ~~ TAggScale_12 + TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_12 ~~ TAggScale_14 + TAggScale_16 + TAggScale_18
TAggScale_14 ~~ TAggScale_16 + TAggScale_18
TAggScale_16 ~~ TAggScale_18

PProScale_1 ~~ PProScale_3 + PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14 +
PProScale_16 + PProScale_18
PProScale_3 ~~ PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14 +
PProScale_16 + PProScale_18
PProScale_5 ~~ PProScale_10 + PProScale_12 + PProScale_14 + PProScale_16 + PProScale_18
PProScale_10 ~~ PProScale_12 + PProScale_14 + PProScale_16 + PProScale_18
PProScale_12 ~~ PProScale_14 + PProScale_16 + PProScale_18
PProScale_14 ~~ PProScale_16 + PProScale_18
PProScale_16 ~~ PProScale_18

TProScale_1 ~~ TProScale_3 + TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14 +
TProScale_16 + TProScale_18
TProScale_3 ~~ TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14 +
TProScale_16 + TProScale_18
TProScale_5 ~~ TProScale_10 + TProScale_12 + TProScale_14 + TProScale_16 + TProScale_18
TProScale_10 ~~ TProScale_12 + TProScale_14 + TProScale_16 + TProScale_18
TProScale_12 ~~ TProScale_14 + TProScale_16 + TProScale_18
TProScale_14 ~~ TProScale_16 + TProScale_18
TProScale_16 ~~ TProScale_18
'

mod.5 <- '
##define latent variables
peer1 =~ L1*PPeerScale_1 + L2*TPeerScale_1
peer2 =~ L1*PPeerScale_3 + L2*TPeerScale_3
peer3 =~ L1*PPeerScale_5 + L2*TPeerScale_5
peer4 =~ L1*PPeerScale_10 + L2*TPeerScale_10
peer5 =~ L1*PPeerScale_12 + L2*TPeerScale_12
peer6 =~ L1*PPeerScale_14 + L2*TPeerScale_14

agg1 =~ L1*PAggScale_1 + L2*TAggScale_1
agg2 =~ L1*PAggScale_3 + L2*TAggScale_3
agg3 =~ L1*PAggScale_5 + L2*TAggScale_5
agg4 =~ L1*PAggScale_10 + L2*TAggScale_10
agg5 =~ L1*PAggScale_12 + L2*TAggScale_12
agg6 =~ L1*PAggScale_14 + L2*TAggScale_14

pro1 =~ L1*PProScale_1 + L2*TProScale_1
pro2 =~ L1*PProScale_3 + L2*TProScale_3
pro3 =~ L1*PProScale_5 + L2*TProScale_5
pro4 =~ L1*PProScale_10 + L2*TProScale_10
pro5 =~ L1*PProScale_12 + L2*TProScale_12
pro6 =~ L1*PProScale_14 + L2*TProScale_14

## free latent variances at later times (only set the scale once)
peer2 ~~ NA*peer2
peer3 ~~ NA*peer3
peer4 ~~ NA*peer4
peer5 ~~ NA*peer5
peer6 ~~ NA*peer6

agg2 ~~ NA*agg2
agg3 ~~ NA*agg3
agg4 ~~ NA*agg4
agg5 ~~ NA*agg5
agg6 ~~ NA*agg6

pro2 ~~ NA*pro2
pro3 ~~ NA*pro3
pro4 ~~ NA*pro4
pro5 ~~ NA*pro5
pro6 ~~ NA*pro6

peer1 ~~ agg1 + pro1
agg1 ~~ pro1
peer2 ~~ agg2 + pro2
agg2 ~~ pro2
peer3 ~~ agg3 + pro3
agg3 ~~ pro3
peer4 ~~ agg4 + pro4
agg4 ~~ pro4
peer5 ~~ agg5 + pro5
agg5 ~~ pro5
peer6 ~~ agg6 + pro6
agg6 ~~ pro6

## directional regression paths
peer2 ~ peer1 + agg1 + pro1
agg2 ~ peer1 + agg1 + pro1
pro2 ~ peer1 + agg1 + pro1

peer3 ~ peer2 + agg2 + pro2
agg3 ~ peer2 + agg2 + pro2
pro3 ~ peer2 + agg2 + pro2

peer4 ~ peer3 + agg3 + pro3
agg4 ~ peer3 + agg3 + pro3
pro4 ~ peer3 + agg3 + pro3

peer5 ~ peer4 + agg4 + pro4
agg5 ~ peer4 + agg4 + pro4
pro5 ~ peer4 + agg4 + pro4

peer6 ~ peer5 + agg5 + pro5
agg6 ~ peer5 + agg5 + pro5
pro6 ~ peer5 + agg5 + pro5

## correlated residuals across time
PPeerScale_1 ~~ PPeerScale_3 + PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_3 ~~ PPeerScale_5 + PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_5 ~~ PPeerScale_10 + PPeerScale_12 + PPeerScale_14
PPeerScale_10 ~~ PPeerScale_12 + PPeerScale_14
PPeerScale_12 ~~ PPeerScale_14

TPeerScale_1 ~~ TPeerScale_3 + TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_3 ~~ TPeerScale_5 + TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_5 ~~ TPeerScale_10 + TPeerScale_12 + TPeerScale_14
TPeerScale_10 ~~ TPeerScale_12 + TPeerScale_14
TPeerScale_12 ~~ TPeerScale_14

PAggScale_1 ~~ PAggScale_3 + PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_3 ~~ PAggScale_5 + PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_5 ~~ PAggScale_10 + PAggScale_12 + PAggScale_14
PAggScale_10 ~~ PAggScale_12 + PAggScale_14
PAggScale_12 ~~ PAggScale_14

TAggScale_1 ~~ TAggScale_3 + TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_3 ~~ TAggScale_5 + TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_5 ~~ TAggScale_10 + TAggScale_12 + TAggScale_14
TAggScale_10 ~~ TAggScale_12 + TAggScale_14
TAggScale_12 ~~ TAggScale_14

PProScale_1 ~~ PProScale_3 + PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14
PProScale_3 ~~ PProScale_5 + PProScale_10 + PProScale_12 + PProScale_14
PProScale_5 ~~ PProScale_10 + PProScale_12 + PProScale_14
PProScale_10 ~~ PProScale_12 + PProScale_14
PProScale_12 ~~ PProScale_14

TProScale_1 ~~ TProScale_3 + TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14
TProScale_3 ~~ TProScale_5 + TProScale_10 + TProScale_12 + TProScale_14
TProScale_5 ~~ TProScale_10 + TProScale_12 + TProScale_14
TProScale_10 ~~ TProScale_12 + TProScale_14
TProScale_12 ~~ TProScale_14
'

#fit.5 <- sem(mod.5, data=data_wide, missing = "FIML", std.lv=TRUE)
#summary(fit.5, standardized=TRUE, fit.measures=TRUE)
```
Converged (but again had to remove the last 2 time points)! It shows a poor fit, but only used 39/306 observations!! When I reran it using FIML for missing data, it ran into an error.

```{r Question 4}
#Longitudinal growth model with a fixed slope
mod.6.fixed <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                 s =~ 0*PPeerScale_1 + 1*PPeerScale_3 + 2*PPeerScale_5 +  3*PPeerScale_10 + 4*PPeerScale_12 + 
                        5*PPeerScale_14 + 6*PPeerScale_16 + 7*PPeerScale_18

                 s ~~ 0*s #fixed slopes, no variance'
fit.6.fixed <- growth(mod.6.fixed, missing = "ML", data = data_wide)
inspect(fit.6.fixed, "cov.lv")
#slope is 0.000

#Longitudinal growth model with a random slope
mod.6.random <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                  s =~ 0*PPeerScale_1 + 2*PPeerScale_3 + 4*PPeerScale_5 +  9*PPeerScale_10 + 11*PPeerScale_12 + 
                        13*PPeerScale_14 + 15*PPeerScale_16 + 17*PPeerScale_18'
fit.6.random <- growth(mod.6.random, missing = "FIML", data = data_wide)


#Calculate a more precise time metric
apply(data_wide[,82:89], 2, mean, na.rm=T)

#Longitudinal growth model with a random slope and more precise time metric
mod.6.precise <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                  s =~ 0*PPeerScale_1 + 1.022622*PPeerScale_3 + 2.012532*PPeerScale_5 +  4.597019*PPeerScale_10 +
                        5.724867*PPeerScale_12 + 6.709552*PPeerScale_14 + 7.955476*PPeerScale_16 + 
                        9.164656*PPeerScale_18'
fit.6.precise <- growth(mod.6.precise, missing = "FIML", data = data_wide)

#Mulitlevel model with a random slope
mod.6.MLM <- lmer(PPeerScale ~ age0 + (age0 | ID), data_long)
summary(mod.6.MLM)
summary(fit.6.precise)
```
The mean estimate from the growth model (intercept= 61.337, and slope= 0.121) differs slightly from the fixed effects of the multilevel model (intercept= 61.1291, slope= 0.1551). The variance of the growth model (intercept= 49.535, slope= 0.826), also differs slightly from the random effect of the multilevel model (intercept= 43.36, slope= 0.8674).


## Question 5
```{r Question 5}
#Longitudinal growth model with a random slope, constraining residual variances to 0
mod.7 <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                  s =~ 0*PPeerScale_1 + 2*PPeerScale_3 + 4*PPeerScale_5 +  9*PPeerScale_10 + 11*PPeerScale_12 + 
                        13*PPeerScale_14 + 15*PPeerScale_16 + 17*PPeerScale_18

PPeerScale_1 ~~ 0*PPeerScale_1
PPeerScale_3 ~~ 0*PPeerScale_3
PPeerScale_5 ~~ 0*PPeerScale_5
PPeerScale_10 ~~ 0*PPeerScale_10
PPeerScale_12 ~~ 0*PPeerScale_12
PPeerScale_14 ~~ 0*PPeerScale_14
PPeerScale_16 ~~ 0*PPeerScale_16
PPeerScale_18 ~~ 0*PPeerScale_18
'
#fit.7 <- growth(mod.7, missing="ML", data=data_wide)
#inspect(fit.7, "cov.lv")
```
Model won't run.


## Question 6
```{r Question 6}
#Longitudinal growth model with a fixed slope
mod.6.fixed <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                 s =~ 0*PPeerScale_1 + 2*PPeerScale_3 + 4*PPeerScale_5 +  9*PPeerScale_10 + 11*PPeerScale_12 + 
                        13*PPeerScale_14 + 15*PPeerScale_16 + 17*PPeerScale_18

                 s ~~ 0*s #fixed slopes, no variance'
fit.6.fixed <- growth(mod.6.fixed, missing = "ML", data = data_wide)
inspect(fit.6.fixed, "cov.lv")
#slope-slope covariance is 0.000
```
Model won't run.


## Question 7
```{r Question 7}
#Longitudinal growth model with a random slope, with a different time metric
mod.6.centered <- ' i =~ 1*PPeerScale_1 + 1*PPeerScale_3 + 1*PPeerScale_5 +  1*PPeerScale_10 + 1*PPeerScale_12 + 
                        1*PPeerScale_14 + 1*PPeerScale_16 + 1*PPeerScale_18
                  s =~ -3*PPeerScale_1 + -2*PPeerScale_3 + -1*PPeerScale_5 +  0*PPeerScale_10 + 1*PPeerScale_12 + 
                        2*PPeerScale_14 + 3*PPeerScale_16 + 4*PPeerScale_18'
fit.6.centered <- growth(mod.6.centered, missing = "FIML", data = data_wide)

summary(fit.6.centered)
summary(fit.6.random)
```
The mean estimates of the intercept and slope changes slightly, since 0 now indicates the mean at the 4th wave rather than the 1st wave. The variance for the intercept and slope also changed slightly, as does the covariance between the intercept and slope. It does not seem to affect the fit statistics though.


## Question 8
```{r Question 8}
fit.8.precise <- growth(mod.6.precise, missing = "FIML", estimator = "MLR", data = data_wide)
summary(fit.8.precise)
summary(fit.6.precise)
```
Changing the estimator to MLR seemed to only add to the fit statistics, adding an extra "Robust" column to indicate the robust goodness of fit.

## Question 9
```{r Question 9}
semPaths(fit.1, what="std")
semPaths(fit.3, what="std")
semPaths(fit.8.precise, what="std")
```
