---
title: "Intensive Longitudinal Analyses"
author: "Brent Rappaport"
date: "October 17, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=F)
rm(list=ls())
library(psych)
library(tidyverse)
library(sjPlot)
library(broom)
library(lme4)
library(MuMIn)
library(merTools)
library(reghelper)
library(stargazer)
library(lsmeans)
library(multcompView)
library(plyr)
library(papaja)
library(stringr)
```
# Adapted from Isidro's presentation and code

##Load in data
```{r load data}
data_wide <- read.csv("/Users/BrentRappaport/Box Sync/WashU/Classes/Longtudinal Methods/1-descriptives-and-graphs-brappaport/Rappaport_data.csv")
data_wide <- data_wide[,-1]

#Make sex_01 a binary variable where 0=Male and 1=Female
data_wide$sex_01 <- data_wide$sex-1

#Make sex_c a factor variable
data_wide$sex_c <- ifelse(data_wide$sex_01==0,"Male","Female")
data_wide$sex_c <- as.factor(data_wide$sex_c)

#Center SES
data_wide$T1Income_to_Need_c <- scale(data_wide$T1Income_to_Need, center=T, scale=F)

#Make age0_ a variable of age from beginning of study (relative age to beginning), rather than aboslute age
data_wide <- data_wide %>%
  mutate(age0_1 = age_1 - age_1,
         age0_3 = age_3 - age_1,
         age0_5 = age_5 - age_1,
         age0_10 = age_10 - age_1,
         age0_12 = age_12 - age_1,
         age0_14 = age_14 - age_1,
         age0_16 = age_16 - age_1,
         age0_18 = age_18 - age_1)

#Convert data to long form
data_long <- data_wide %>% 
  gather(c(-ID,-sex,-sex_01,-sex_c,-T1_ACES_sum,-ethin,-T1Income_to_Need,-T1Income_to_Need_c,-IQ), 
         key = "time", value = "value") %>% 
  separate(time, into = c("variable", "wave")) %>%
  spread(variable,value)

data_long$wave <- as.integer(data_long$wave)

#sort by id
data_long <- data_long[order(data_long$ID),] 
```

##Graph individual trajectories
```{r Graphs}
# Generate a random sample because 150 too many for graph below
set.seed(20)
Peer_24 <- data_long %>% 
  select(ID) %>%  
  distinct %>% 
  sample_n(24)

Peer_data2 <- left_join(Peer_24, data_long) 
  # Use left_join to keep all observations for each time point
  # only for ids that were sampled 

# Fluctuation in peer interactions

ggplot(Peer_data2, aes(age, PPeerScale, group = ID)) + geom_line() + 
  geom_point() + facet_wrap(~ID) + 
  xlab("Age") + ylab("Peer Interactions") + 
  ggtitle("Figure 1. Peer Interactions as a Function of Age") +
  theme_classic() +
  theme(legend.position = "none",
          axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), 
                                    hjust = .5))
```

##Rescale predictors
```{r rescaling predictors}
#Calculate aggregates within a seperate dataframe
# i.e., Mean for each person across their respective time points
long_agg <- data_long %>% 
  group_by(ID) %>%
  summarize(PPeer_agg = mean(PPeerScale, na.rm = T),
            TPeer_agg = mean(TPeerScale, na.rm = T),
            PAgg_agg = mean(PAggScale, na.rm = T),
            TAgg_agg = mean(TAggScale, na.rm = T),
            PPro_agg = mean(PProScale, na.rm = T),
            TPro_agg = mean(TProScale, na.rm = T),
            MDD_agg = mean(MDDPRP, na.rm = T))

# Merge with original dataset
## ISSUE WITH MERGING!!
data_long <- merge(data_long, long_agg, all.x=T)
#full_join(data_long, long_agg, by = "ID")

# Person- and grand mean-center using original and aggregated scores
data_long <- data_long %>% mutate(PPeer_pc = PPeerScale - PPeer_agg,
                   TPeer_pc = TPeerScale - TPeer_agg,
                   PAgg_pc = PAggScale - PAgg_agg,
                   TAgg_pc = TAggScale - TAgg_agg,
                   PPro_pc = PProScale - PPro_agg,
                   TPro_pc = TProScale - TPro_agg,
                   MDD_pc = MDDPRP - MDD_agg,
                   ACES_gm = T1_ACES_sum - mean(T1_ACES_sum, na.rm = T),
                   SES_gm = T1Income_to_Need - mean(T1Income_to_Need, na.rm = T),
                   IQ_gm = IQ - mean(IQ, na.rm = T))
  # Subtract person's mean from their raw score to get person-centered 
  # For ACES, SES, and IQ: grand mean center because they're time-invariant

# Check calculations; should get 'TRUE' if done correctly
all(data_long$PPeerScale == data_long$PPeerScale_pc + data_long$PPeer_agg, na.rm = T) 
```

# Separating sources of variance
```{r Model 1a}
#Unconditional means model (intercept and time only)
mod1a <- lmer(PPeerScale ~ age0 + (1 | ID), data_long)
summary(mod1a)
ICC(mod1a)
```
Model shows that average PPeer score at baseline is 61.13, that increases 0.16 each year.
ICC indicates that there is slightly more between than within-person variance.
```{r Model 1b}
#Concurrent correlation between MDD symptoms and PPeer scores
mod1b <- lmer(PPeerScale ~ age0 + MDDPRP + (1 | ID), data_long)
summary(mod1b)
```
Intercept (mean at baseline) is mostly unchanged (61.37), as is the slope (0.11 increase in PPeer every year). An increase in MDDPRP predicts a huge decline in PPeer score, of -20.28.
```{r Model 1c}
# Now including aggregated (between) person-centered (within) MDD
mod1c <- lmer(PPeerScale ~ age0 + MDD_agg + MDD_pc + (1 | ID), data_long)
summary(mod1c)
```
NOT WORKING: too much missing data

##Examining predictions from wave to wave
###Setup data to be lagged
```{r Lag data}
data_long %<>% mutate(PPeer_prev = lag(PPeerScale),
                   MDD_prev = lag(MDDPRP),
                   PPeer_pc_prev = lag(PPeer_pc),
                   MDD_pc_prev = lag(MDD_pc),
                   PPeer_pc_prev2 = lag(PPeer_pc, n = 2),
                   MDD_pc_prev2 = lag(MDD_pc, n = 2)) %>%
  select(MDDPRP, MDD_prev, ID, wave, PPeerScale, PPeer_prev, everything())
data_long$MDD_pc_prev[data_long$wave == 1] <- NA
data_long$PPeer_pc_prev[data_long$wave == 1] <- NA
data_long$MDD_pc_prev2[data_long$wave == 1] <- NA
data_long$PPeer_pc_prev2[data_long$wave == 1] <- NA
```

##Time-lagged models
```{r Time-lagged models}
# Does MDD predict PPeer controlling for previous wave's PPeer?
mod2a <- lmer(PPeerScale ~ age0 + PPeer_pc_prev + MDD_pc_prev + 
                (1 | ID), data_long)
summary(mod2a)
# Yes, a one unit increase in MDD symptoms results in a average decrease of 15.25 on PPeer.

# What about including both between- and person-centering
mod2ab <- lmer(PPeerScale ~ age0 + PPeer_pc_prev + MDD_pc_prev + MDD_agg + 
                 (1 + MDD_pc_prev | ID), data_long)
summary(mod2ab)

# Correlation between PPeer and pc MDD
mod2ac <- lmer(MDDPRP ~  MDD_agg + (1 | ID), data_long)
summary(mod2ac)
```
